Think deep for reef resilience

### 2025-09-25 paper/paper_draft.qmd
Add RF performance metrics

>>>>

## Random Forest Performance

|               |         |                  |          |
|---------------|---------|------------------|----------|
|               |         | **Ground Truth** |          |
| **Predicted** | **Low** | **Medium**       | **High** |
| **Low**       | 1371    | 682              | 151      |
| **Medium**    | 247     | 603              | 340      |
| **High**      | 97      | 302              | 787      |

: Confusion matrix for the Random Forest classifier used to assess partial dependence.
Diagonals indicate correctly classified time series clusters. Columns are the "true" cluster
memberships and indicate the samples that were correctly or incorrectly classified as
Low/Medium/High. For example, the first column shows the number of samples correctly
classified into the Low cluster, and the number of Low samples incorrectly classified as
being in either the Medium or High coral cover clusters. There were 4580 samples used for
testing.

|              |         |            |          |
|--------------|---------|------------|----------|
|              | **Low** | **Medium** | **High** |
| Test samples | 1715    | 1587       | 1278     |
| Precision    | 0.622   | 0.507      | 0.664    |
| Recall       | 0.799   | 0.38       | 0.616    |
| F1           | 0.7     | 0.434      | 0.639    |

: Performance metrics for the Random Forest classifier for each of the time series clusters.
